Comparing vector-based and ACT-R memory models of tag retrieval:\protect\\User-customized hashtag/tag prediction on Twitter and StackOverflow

### 2014-07-30 writeups/dissertation/dissertation.tex
foo

Finally, model accuracy was analyzed across all dataset slices for StackOverflow and Twitter.
Mean accuracy for both sites is included in Figure \ref{figPriorAcc}. 
The mean was computed by taking the mean of the mean model accuracy for each dataset slice.
All confidence intervals are 95\% bootstrapped for the mean of the means for each slice.

@@

The best-fit decay rate values were also analyzed across all dataset slices.
These results are included in Figure \ref{figPriorDecay}.

@@

The mean was computed by taking the mean of the median best-fit decay rate value for each dataset slice.
The median was used since the distribution of best-fit decay rate values for each dataset slice is somewhat positively skewed (e.g., the histograms in Figures \ref{figPriorSOQHistDsOL} and \ref{figPriorTwitterHistDsOL}).
Also, there were users in the popular-users dataset that did not have enough observations to generate stable predictions, and best-fit decay rate values for these users could be as high as 20.
Using the median effectively trims these unstable values from the sample, without having to define a cut point and go through an outlier removal process.

@@

The impact of adding the offset to each of the models for StackOverflow and Twitter are included in Figures \ref{figContextOffsetSO} and \ref{figContextOffsetT}.

>>>>

Finally, model accuracy was analyzed across all dataset slices for StackOverflow and Twitter.
Accuracy for both sites is included in Figure \ref{figPriorAcc}. 
Aggregate accuracy was computed by taking the mean of every user's model accuracy across all users in all dataset slices.
All confidence intervals are 95\% bootstrapped for the mean.

@@

The best-fit decay rate values were also analyzed across all dataset slices.
Aggregate best-fit decay rates were computed by taking the median of all user's best-fit decay rate value across all dataset slices.
The median was used since there were users in the popular-users dataset that did not have enough observations to generate stable predictions, and best-fit decay rate values for these users could be as high as 20.
Using the median effectively trims these unstable values from the sample, without having to define a cut point and go through an outlier removal process.

These results are included in Figure \ref{figPriorDecay}.
Error bars represent the 95\% bootstrapped confidence interval of the median.

@@

@@

The impact of adding the offset to each of the models for StackOverflow and Twitter are included in Figures \ref{figContextOffsetSO} and \ref{figContextOffsetT}.
The error bars represent the 95\% bootstrapped confidence interval of the mean model accuracy across all runs in dataset.
